\chapter{Vision}

JassTracker is a web app which allows tracking and analysis of the popular Swiss card game \gls{jass}.
There are many different forms of playing, but the one we're focusing on is called "Coiffeur".
The following paragraphs expect the reader to know the basic rules and concepts of a "Coiffeur Jass".

\section*{What It Does}
The goal of the JassTracker is to allow the players to focus on the game without having to worry about tracking points or whose turn it is.
Instead of having to write down the scores using pen and paper, you can simply input them into the JassTracker digitally.
The website automagically tracks whose turn it is and analyses your scores for you.
You can also gain exhaustive insight into your play style by looking at personal or group statistics, such as average score by player or historic averages.
The system is also very flexible and can be configured to your liking.
For example, once you have configured a Jass table, you can easily start a new game with the same players.

\section*{How It Works}
The fist step is to create a new table and enter all team members for the game.
Then you start playing the game physically, just like you would normally.
Once a round is over, you input the score for the scoring member and "Trumpf".
After entering the points, a few things happen automatically:
\begin{itemize}
    \item Player \& team score update
    \item The upcoming starting person is shown
    \item Statistics refresh with latest information
\end{itemize}
When the game has finished, highlights of the game (e.g. the best player or highest round score) are displayed.

\section*{Extensions}
Some potential ideas to expand on:
\begin{itemize}
    \item Configurable Jass game (e.g. Coiffeur with 8 instead of 10 options)
    \item Prediction of scores based on historic performance
    \item Current game trajectory (win probability by team)
    \item Share the scoreboard in real time with other members, in case you want to show the scoreboard on a different device as well
    \item Associate game to personal account to track personal statistics across games
    \item In depth statistics like play style, favorite "Trumpf", best "partner" by win probability etc.
    \item Charts in game to show statistics
\end{itemize}
